Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-25 Response/Response 2/response-1.tex

\vspace{1eM}
\underline{\textit{Reply:}} We thank the reviewer for providing valuable and insightful comments.

\vspace{1eM}
For the resubmitted manuscript, the reviewer still has the following concerns

\begin{enumerate}
\cmnt{1} \review{Considering the length of the manuscript, it would be better to shorten some parts that are not new in this manuscript, e.g. III.A. More space can be left for convergence proof, which is very important. }

\resp After a careful check of the manuscript, we have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details for the convergence proof. We believe the removed parts do not affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.

@@

\cmnt{2} \review{In convergence proof (48), why does the 2nd inequality hold? In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, \eqn{\leq 0} directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore feasible.  }

\resp We thank the reviewer for the critical comment. Based on the comment by the reviewer, we have removed the additional inequality relating the previous operating point from (49) in the revised manuscript.

@@

\cmnt{3} \review{The solutions SCA iterations \eqn{\mbf{m}^{(i)}_k} does not necessarily converge. In fact \eqn{\mbf{m}} has compact feasible region, and thus \eqn{\mbf{m}^{(i)}_k} has limit points for any specific \eqn{i}.  However \eqn{m_{*}^{(i)}} does not necessarily exist( the whole sequence \eqn{\mbf{m}^{(i)}_k} may be not convergent). Similar problem happens to \eqn{\mbf{w}^{(i)}_k}. }

\resp  We thank the reviewer for citing the issue regarding the sequence convergence. Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge. It follows from the convexity of the original function, which can have multiple solutions. However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32], which ensures the uniqueness of the solution in each \ac{SCA} update.

Since our problem is (highly) nonconvex and there are possibly many stationary points. If we start from different initial points, we may end up with different stationary points. That is to say, the limit point of \ac{SCA} approach is not unique. However, by regularizing the objective with a small quadratic term, the iterate in each step of \ac{SCA} algorithm is unique. This and the fact that the set is compact ensure the \ac{SCA} converges to a limit point. We have updated the manuscript to include this information in the convergence proof for the centralized algorithm in Appendix A. The modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).

@@

\cmnt{4} \review{Strict monotonicity with respect to the objective function \eqn{f} should be rigorously proved. Note that to guarantee the uniqueness of the beamformer iterates, (52) instead of the objective function is used.}

\resp We thank the reviewer for the pointing out the issue involving the strict monotonicity. As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52). Moreover, we have also noted the reader that we in fact use the regularized objective in (46b) to analytically prove the convergence of iterates, although we have numerically observed that the objective sequence of Algorithm 1 (with the original objective) always converge. Please refer to the paragraph before Section III-C.

### 2015-07-25 Report/convergence_centralized.tex
to read

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point \cite{meyer1976sufficient}. Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limit point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} step index by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}. Let \eqn{\mx_k^{(i)}} denotes the stacked transmit precoders of all users at the \eqn{\ith{k}} \ac{SCA} step in the \eqn{\ith{i}} \ac{AO} iteration.

@@

\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness is not guaranteed since there can be many solutions satisfying the constraints with the same objective value. Similarly, when the objective is non-zero for  \eqref{eqn-9}, the minimizer is unique, if the receivers are matched to the corresponding transmit beamformers. %, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \tfrac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees the unique minimizer \cite{yang_yang}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}. The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e.}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
%
%When the objective is zero, the uniqueness of the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum. To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
%\begin{equation}
%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
%\end{equation}
%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant. The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration. %Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}. The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e.}, unitary transformations. When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems. To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.

@@

To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}. In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as

@@

Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications. Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
\end{equation}
The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the \ac{DC} constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
\begin{equation} \label{rhs_equiv}
\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
\end{equation}
Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}. By using \cite[Th. 2 and 11]{scutari_1} or \cite[Prop. 3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the original nonconvex problem in \eqref{con}.}

>>>>

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point \cite{meyer1976sufficient}. Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limit point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. However, after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,scutari-1} by relaxing \eqref{con-dc} by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when \ac{SCA} converges in the \me{\ith{i}} \ac{AO} step and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} in the \me{\ith{i}} \ac{AO} step for fixed \me{\my}. The stacked transmit precoders of all users in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} is given by \eqn{\mx_k^{(i)}}.

@@

\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set. Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers. %, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of the objective with some parameter \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} and \eqn{m > 0} as discussed in \cite{scutari-1}. Now by using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}. The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e.}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
%of the objective
%When the objective is zero, the uniqueness of  the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum. To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
%\begin{equation}
%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
%\end{equation}
%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant. The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration. %Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}. The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e.}, unitary transformations. When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems. To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.

@@

To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}. In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as

@@

Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications. Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
\end{equation}
The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
\begin{equation} \label{rhs_equiv}
\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
\end{equation}
Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}. By using \cite[Th. 2 and 11]{scutari_1} or \cite[Prop. 3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the original nonconvex problem in \eqref{con}.}

### 2015-07-25 Report/convergence_distributed.tex
to read

\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible. The objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, and therefore exhibits strong convexity. The feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Therefore, by following \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed}, it can be shown that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.

If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence is a stationary point of \eqref{con}, using Appendix \ref{sec-3.5}. However, if the distributed algorithms are terminated well before the convergence or performed for few number of iterations, say, \eqn{J_{\max}}, then the convergence of the iterates \me{\{\ma^{(i)}\}} is not guaranteed. It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed schemes for \eqref{con-m} are updated for sufficient number iterations to ensure strict monotonicity in each \ac{SCA} step, then the limit point of \me{\{\ma^{(i)}\}} is a stationary point of \eqref{con}, which can be different from the one obtained by solving \eqref{con-m} with \eqn{J_{\max} = \infty}.}

%\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, say, \eqn{J_{\max}}, the convergence of the sequence \me{\{\ma^{(i)}\} \triangleq \{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is not guaranteed. It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence. If the distributed algorithm is iterated sufficient number of times to ensure strict monotonicity of the objective in each \ac{SCA} step with the modified function \eqref{mod_obj}, then the limit point of the convergent sequence is a stationary point of \eqref{con}, which can be different from the limit point obtained by solving the centralized solution.}

	%Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity and the convergence of the objective is not guaranteed unless the number of iterations is large enough to have strictly decreasing objective. Moreover, monotonicity of the global objective in each primal or \ac{ADMM} update is not ensured, despite reaching the centralized solution upon convergence.}

@@

However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence. \review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the Algorithm \ref{algo-4} to a stationary point of \eqref{eqn-mse-1} is not guaranteed. In addition, due to the convexity of the objective in \eqref{eqn-mse-1}, the sequence of iterates generated by Algorithm \ref{algo-4} need not be convergent.} However, the objective converges in all numerical experiments considered in Section \ref{sec-5.2}.

>>>>

\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing the problem as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible. The objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size. If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments in Appendix \ref{sec-3.5}. }

%However, if the distributed algorithms are terminated well before the convergence or performed for few number of iterations, say, \eqn{J_{\max}}, then the convergence of the iterates \me{\{\ma^{(i)}\}} is not guaranteed. It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed schemes for \eqref{con-m} are updated for sufficient number iterations to ensure strict monotonicity in each \ac{SCA} step, then the limit point of \me{\{\ma^{(i)}\}} is a stationary point of \eqref{con}, which can be different from the one obtained by solving \eqref{con-m} with \eqn{J_{\max} = \infty}.}
%\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, say, \eqn{J_{\max}}, the convergence of the sequence \me{\{\ma^{(i)}\} \triangleq \{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is not guaranteed. It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence. If the distributed algorithm is iterated sufficient number of times to ensure strict monotonicity of the objective in each \ac{SCA} step with the modified function \eqref{mod_obj}, then the limit point of the convergent sequence is a stationary point of \eqref{con}, which can be different from the limit point obtained by solving the centralized solution.}
%If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence is a stationary point of \eqref{con}, using Appendix \ref{sec-3.5}. However, if the distributed algorithms are terminated well before the convergence or performed for few number of iterations, say, \eqn{J_{\max}}, then the convergence of the iterates \me{\{\ma^{(i)}\}} is not guaranteed. It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed schemes for \eqref{con-m} are updated for sufficient number iterations to ensure strict monotonicity in each \ac{SCA} step, then the limit point of \me{\{\ma^{(i)}\}} is a stationary point of \eqref{con}, which can be different from the one obtained by solving \eqref{con-m} with \eqn{J_{\max} = \infty}.}
%Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity and the convergence of the objective is not guaranteed unless the number of iterations is large enough to have strictly decreasing objective. Moreover, monotonicity of the global objective in each primal or \ac{ADMM} update is not ensured, despite reaching the centralized solution upon convergence.}

@@

However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence. \review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, note that the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update. Due to this reason, the algorithm cannot find a fixed point to ensure the convergence of the beamformer iterates.}
